Assessment of forestry road network projection methods using the “roads” package in R

### 2022-08-26 analysis/paper/paper.Rmd
add ft nelson results

>>>>

## Fort Nelson map

```{r ftNelson, fig.height=6, fig.width=fig_widths["two"], fig.cap="Road projections for the Fort Nelson Timber Supply Area. Black lines show projected and pre-existing roads. Red lines show observed roads that were not captured by the projections."}
ftN_roads_proj <- read_sf(here("analysis/data/derived_data/TSA8_1000/centroid_1e-05.shp"))

ftN_roads_obs <- read_sf(here("analysis/data/derived_data/combined_ft_nelson_roads.gpkg"))

qtm(ftN_roads_obs, lines.col = "red")+
  qtm(ftN_roads_proj)
```
